%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Work Experience}


%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {AVP(Lead Software Engineer)} % Job title
    {Barclays Global Service Centre Pvt. Ltd.} % Organization
    {Chennai, Tamilnadu, India} % Location
    {Feb. 2020 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Architected \& Implemented in-memory reconciliation system from scratch to process high volume intersystem reconciliations}
        \item {Developed in-memory matching engine to match records with high performance comparing legacy systems}
        \item {Designed the integration of legacy reconciliation system to report the breaks for management}
        \item {Helped the teams to identify and mitigate age old tech debt items}
        \item {Helped the teams to upgrade Java from older versions and fix issues related to it}
        \item {Redesigned the applications and helped the team to mitigate flash EOL within a short span which had huge business impact}
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Application Developer Intermediate Programmer Analyst(Senior Software Engineer)} % Job title
    {Citicorp Services India Pvt. Ltd.} % Organization
    {Chennai, Tamilnadu, India} % Location
    {Oct. 2016 - Feb. 2020} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed real-time reconciliation data pipeline using Lambda architecture to crunch billions of records}
        \item {Redesigned matching layer to achieve 12k messages/sec with sub milli second latency}
        \item {Migrated the transformation layer from batch to streaming platform (Storm/Kafka) to provide 6X higher performance}
        \item {Built \& deployed the real-time break management system using Elastic stack to reduce report timing from minutes to seconds}
        \item {Designed \& Implemented the initial version of CI/CD pipeline using TeamCity and Urbancode Deploy}        
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Associate Consultant} % Job title
    {Infrasoft Technologies Ltd. (Client - BNP Paribas Securities Ltd.)} % Organization
    {Chennai, Tamilnadu, India} % Location
    {Sep. 2015 - Oct. 2016} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Implemented multiple new features to collect and process SWIFT messages from multiple sources every day}
        \item {Helped the team to identify and fix critical bugs in Corporate action straight through processes}        
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Senior Application Developer} % Job title
    {BNY Mellon Technology Pvt. Ltd. (Inautix)} % Organization
    {Chennai, Tamilnadu, India} % Location
    {Aug. 2011 - Sep. 2015} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed template configuration management system to ease the initial account setup process}
        \item {Lead the integration of Advisor model management system with New account opening system using RESTful webservices}
        \item {Fixed some of the performance bottlenecks with the help of Dynatrace reports}
      \end{cvitems}
    }
%--------------------------------------------------------- 
\end{cventries}
